Lapse & Vision Loss PS Analysis

### 2025-02-24 analysis.Rmd
wip

library(readr)
library(dplyr)
library(kableExtra)
library(purrr)
library(gee)
library(geepack)
library(ggplot2)
library(MatchIt)
library(twang)
library(survey)
library(cobalt)
library(margins)

@@

    if (params$method == "twang") {
      result <- tryCatch({
        ps(formula = formula, data = data.frame(data), 
           n.trees = 10000,
           interaction.depth = 3,
           shrinkage = 0.01,
           estimand = params$estimand,
           stop.method = c("es.mean", "ks.max"))  # Stopping criteria
      }, error = function(e) {
        message("Error in TWANG GBM: ", e)
        return(NULL)
      })

      if (!is.null(result)) {
        diagnostic_plot <- tryCatch({
          love.plot(result, stat = "mean.diffs", var.order = "es.mean", stars="std")
        }, error = function(e) {
          message("Error generating TWANG balance plot: ", e)
          NULL
        })

        equipoise_plot <- tryCatch({
          bal.plot(result, var.name = "prop.score.es.mean", which="both")
        }, error = function(e) {
          message("Error generating TWANG equipoise plot: ", e)
          NULL
        })

@@

    } else if(length(params$use) > 0 && params$use == "weightit") {
       result <- tryCatch({
        do.call(weightit, c(list(formula = formula, data = data), params))
      }, error = function(e) {
        message("Error in ", params$name, ": ", e)
        return(NULL)
      })

@@

      diagnostic_plot <- tryCatch({
        love.plot(result, stat = "mean.diffs", var.order = "adjusted", stars="std")
      }, error = function(e) {
        message("Error generating diagnostic plot for ", params$name, ": ", e)
        NULL
      })

      if(! params$method %in% c("nearest_mahalanobis", "cem", "cbps", "entropy")) {
        equipoise_plot <- tryCatch({
          bal.plot(result, var.name = "distance", which = "both")
        }, error = function(e) {
          message("Error generating equipoise plot for ", params$name, ": ", e)
          NULL
        })
      } else {
        equipoise_plot <- NULL
      }

      balance_summary <- tryCatch({
        bal.tab(result)
      }, error = function(e) {
        message("Error generating balance summary for ", params$name, ": ", e)
        NULL
      })
    } else {
      result <- tryCatch({
        do.call(matchit, c(list(formula = formula, data = data), params))
      }, error = function(e) {
        message("Error in ", params$name, ": ", e)
        return(NULL)
      })

@@

      diagnostic_plot <- tryCatch({
        love.plot(result, stat = "mean.diffs", var.order = "adjusted", stars="std")
      }, error = function(e) {
        message("Error generating diagnostic plot for ", params$name, ": ", e)
        NULL
      })

      if(! params$method %in% c("nearest_mahalanobis", "cem")) {
        equipoise_plot <- tryCatch({
          bal.plot(result, var.name = "distance", which = "both")
        }, error = function(e) {
          message("Error generating equipoise plot for ", params$name, ": ", e)
          NULL
        })
      } else {
        equipoise_plot <- NULL
      }

@@

    method_results <- list(
      result = result,
      diagnostic_plot = diagnostic_plot,
      equipoise_plot = equipoise_plot,
      summary = balance_summary
    )

@@

```{r diagnostic_plots}
for (method_name in method_names) {
  # Get diagnostic and equipoise plots for the method
  method_results <- results[[method_name]]
  diagnostic_plot <- method_results$diagnostic_plot
  equipoise_plot <- method_results$equipoise_plot

  # Output section header for diagnostic plot
  if (!is.null(diagnostic_plot)) {
    cat("### Diagnostic Plot for", method_name, "\n\n")
    print(diagnostic_plot)
    cat("\n\n")
  }

  # Output section header for equipoise plot (if exists)
  if (!is.null(equipoise_plot)) {
    cat("### Equipoise Plot for", method_name, "\n\n")
    print(equipoise_plot)
    cat("\n\n")
  }
}
```

>>>>

library(readr)
library(dplyr)
library(kableExtra)
library(purrr)
library(gee)
library(geepack)
library(ggplot2)
library(MatchIt)
library(twang)
library(survey)
library(cobalt)
library(margins)
library(margins)

@@

    # For Twang
    if (params$method == "twang") {
      result <- tryCatch({
        ps(formula = formula, data = data.frame(data), 
           n.trees = 10000,
           interaction.depth = 3,
           shrinkage = 0.01,
           estimand = params$estimand,
           stop.method = c("es.mean", "ks.max"))  # Stopping criteria
      }, error = function(e) {
        message("Error in TWANG GBM: ", e)
        return(NULL)
      })

      if (!is.null(result)) {
        balance_plot <- tryCatch({
          love.plot(result, stat = "mean.diffs", var.order = "es.mean", stars="std")
        }, error = function(e) {
          message("Error generating TWANG balance plot: ", e)
          NULL
        })

        common_support_plot <- tryCatch({
          bal.plot(result, var.name = "prop.score.es.mean", which="both")
        }, error = function(e) {
          message("Error generating TWANG common support plot: ", e)
          NULL
        })

@@

    } 
    # For WeightIt
    else if(length(params$use) > 0 && params$use == "weightit") {
       result <- tryCatch({
        do.call(weightit, c(list(formula = formula, data = data), params))
      }, error = function(e) {
        message("Error in ", params$name, ": ", e)
        return(NULL)
      })

@@

      balance_plot <- tryCatch({
        love.plot(result, stat = "mean.diffs", var.order = "adjusted", stars="std")
      }, error = function(e) {
        message("Error generating balance plot for ", params$name, ": ", e)
        NULL
      })

      if(! params$method %in% c("nearest_mahalanobis", "cem", "cbps", "entropy")) {
        common_support_plot <- tryCatch({
          bal.plot(result, var.name = "distance", which = "both")
        }, error = function(e) {
          message("Error generating common support plot for ", params$name, ": ", e)
          NULL
        })
      } else {
        common_support_plot <- NULL
      }

      balance_summary <- tryCatch({
        bal.tab(result)
      }, error = function(e) {
        message("Error generating balance summary for ", params$name, ": ", e)
        NULL
      })
    }
    # For MatchIt
    else {
      result <- tryCatch({
        do.call(matchit, c(list(formula = formula, data = data), params))
      }, error = function(e) {
        message("Error in ", params$name, ": ", e)
        return(NULL)
      })

@@

      balance_plot <- tryCatch({
        love.plot(result, stat = "mean.diffs", var.order = "adjusted", stars="std")
      }, error = function(e) {
        message("Error generating balance plot for ", params$name, ": ", e)
        NULL
      })

      if(! params$method %in% c("nearest_mahalanobis", "cem")) {
        common_support_plot <- tryCatch({
          bal.plot(result, var.name = "distance", which = "both")
        }, error = function(e) {
          message("Error generating common support plot for ", params$name, ": ", e)
          NULL
        })
      } else {
        common_support_plot <- NULL
      }

@@

    method_results <- list(
      result = result,
      balance_plot = balance_plot,
      common_support_plot = common_support_plot,
      summary = balance_summary
    )

@@

```{r balance_plots}
for (method_name in method_names) {
  # Get balance and common support plots for the method
  method_results <- results[[method_name]]
  balance_plot <- method_results$balance_plot
  common_support_plot <- method_results$common_support_plot

  # Output section header for balance plot
  if (!is.null(balance_plot)) {
    cat("### Diagnostic Plot for", method_name, "\n\n")
    print(balance_plot)
    cat("\n\n")
  }

  # Output section header for common support plot (if exists)
  if (!is.null(common_support_plot)) {
    cat("### Equipoise Plot for", method_name, "\n\n")
    print(common_support_plot)
    cat("\n\n")
  }
}
```
